19Q2

### 2019-06-10 19Q2.Rmd

# Edit mutation column
g2p <- add_column(g2p, Mutation_Curated = NA, .after = "Mutation")
g2p$Mutation_Curated <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
g2p$Mutation_Curated <- ifelse(g2p$Mutation_Curated == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Mutation_Curated))
g2p$Mutation_Curated <- gsub(":| |c\\..*", "", g2p$Mutation_Curated)
g2p$Mutation_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Mutation_Curated), pattern = "exon|expression|frameshift|fusion|methylation|mutation")[,1]), NA, as.character(g2p$Mutation_Curated))
g2p$Mutation_Curated <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Mutation_Curated)
g2p$Mutation_Curated <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Mutation_Curated)
g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Mutation_Curated")
g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Mutation_Curated), paste0(as.character(g2p$Gene), ":", as.character(g2p$Mutation_Curated)), NA)

@@

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- filter(g2p, !is.na(Drug)) %>% group_split(biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_mut <- g2p_split[[4]]
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
g2p_nodrug <- filter(g2p, is.na(Drug))
```

@@

```{r load_fusion_data}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)

Merge protein changes: **NEED TO MAKE G2P_prot DATAFRAME (6/4/19)**
```{r merge_protein_changes, eval=FALSE}
ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")
maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")

ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Protein_Change" = unique(maf_changes_df$Protein_Change))
ccle_prot <- merge(merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE), maf_changes_df, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "Protein_Change"), all = TRUE)
ccle_prot$Protein_Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
ccle_prot$Drug_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Protein_Change))
# ccle_prot$G2P_Drug_Protein_Change <- ifelse(ccle_prot$Drug_Protein_Change %in% unique(as.character(g2p_prot$Drug_Protein_Change)), "Yes", "No")
# ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Protein_Change %in% unique(as.character(g2p_prot$Protein_Change)), "Yes", "No")
ccle_prot$Database <- "CCLE"

@@

WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
  require(ggpubr)
  if("Drug_Gene_Lin" %in% grouping) {
    # Filter out DGLs with too few samples in at least one mutation status category
    # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
  }
  if("FusionPair" %in% grouping) {
    # Filter out fusions with too few samples in at least one category
    # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
    count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug, FusionPair, Drug_FusionPair) %>% filter(n == 2)
    keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
    dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
    dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")
  }
  if("Drug_Gene" %in% grouping) {
    # Filter out DGs with too few samples in at least one mutation status category
    # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
    count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
    dataframe <- filter(dataframe, Drug_Gene %in% dgl_keep)
    dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
  }
  signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
  saveRDS(signif, outfile)
  return(signif)
}
```

@@

@@

    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid < -log10(0.05)] <- NA

@@

>>>>

# Edit mutation column
g2p <- add_column(g2p, Protein_Change = NA, .after = "Mutation")
g2p$Protein_Change <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
g2p$Protein_Change <- ifelse(g2p$Protein_Change == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Protein_Change))
g2p$Protein_Change <- gsub(":| |c\\..*", "", g2p$Protein_Change)
g2p$Protein_Change <- ifelse(!is.na(str_match(string = tolower(g2p$Protein_Change), pattern = "exon|expression|frameshift|fusion|methylation|mutation|-")[,1]), NA, as.character(g2p$Protein_Change))
g2p$Protein_Change <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Protein_Change)
g2p$Protein_Change <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Protein_Change)
g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Protein_Change")
g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Protein_Change), paste0(as.character(g2p$Gene), ":", as.character(g2p$Protein_Change)), NA)

@@

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- filter(g2p, !is.na(Drug)) %>% group_split(biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_mut <- g2p_split[[4]]
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
g2p_nodrug <- filter(g2p, is.na(Drug))
g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(group_general_lineage_name, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, paste0(Drug, "_", Gene_Protein_Change))
g2p_prot$Drug_Gene_Protein_Change_Direction <- with(g2p_prot, paste0(Drug_Gene_Protein_Change, "_", Direction_Curated))
```

@@

```{r load_fusion_data}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
```

Merge protein changes
```{r merge_protein_changes, eval=FALSE}
ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")
maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)))

# CCLE
ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
ccle_prot <- merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE)
ccle_prot <- merge(ccle_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
ccle_prot$Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
ccle_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Gene_Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Gene_Protein_Change))
ccle_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ccle_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
ccle_prot <- merge(ccle_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
ccle_prot$Database <- "CCLE"
ccle_prot <- ccle_prot %>% drop_na(Drug)

# CTRP
ctrp_prot_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
ctrp_prot <- merge(ctrp_all, ctrp_prot_grid, by = "DepMap_ID", all = TRUE)
ctrp_prot <- merge(ctrp_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
ctrp_prot$Change_Status <- ifelse(!is.na(ctrp_prot$Protein_Change), "Yes", "No")
ctrp_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ctrp_prot$Drug) | is.na(ctrp_prot$Gene_Protein_Change), NA, paste0(ctrp_prot$Drug, "_", ctrp_prot$Gene_Protein_Change))
ctrp_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ctrp_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
ctrp_prot$G2P_Protein_Change <- ifelse(ctrp_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
ctrp_prot <- merge(ctrp_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
ctrp_prot$Database <- "CTRP"
ctrp_prot <- ctrp_prot %>% drop_na(Drug)

# GDSC
gdsc_prot_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
gdsc_prot <- merge(gdsc_all, gdsc_prot_grid, by = "DepMap_ID", all = TRUE)
gdsc_prot <- merge(gdsc_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
gdsc_prot$Change_Status <- ifelse(!is.na(gdsc_prot$Protein_Change), "Yes", "No")
gdsc_prot$Drug_Gene_Protein_Change <- ifelse(is.na(gdsc_prot$Drug) | is.na(gdsc_prot$Gene_Protein_Change), NA, paste0(gdsc_prot$Drug, "_", gdsc_prot$Gene_Protein_Change))
gdsc_prot$G2P_Drug_Gene_Protein_Change <- ifelse(gdsc_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
gdsc_prot$G2P_Protein_Change <- ifelse(gdsc_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
gdsc_prot <- merge(gdsc_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
gdsc_prot$Database <- "GDSC"
gdsc_prot <- gdsc_prot %>% drop_na(Drug)

prot <- bind_rows(ccle_prot, ctrp_prot, gdsc_prot)
saveRDS(prot, "./data_munging/rds/protein_changes_merged.rds")
```

```{r load_prot_data}
prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
prot_summary <- prot %>% count(Database, Drug, Gene_Protein_Change, Change_Status)
```

@@

WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
  require(ggpubr)
  if("Drug_Gene_Lin" %in% grouping) {
    # Filter out DGLs with too few samples in at least one mutation status category
    # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
  }
  if("FusionPair" %in% grouping) {
    # Filter out fusions with too few samples in at least one category
    # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
    count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug, FusionPair, Drug_FusionPair) %>% filter(n == 2)
    keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
    dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
    dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")
  }
  if("Gene_Protein_Change" %in% grouping) {
    # Filter out Gene:Protein_Changes with too few samples in at least one category
    # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
    count_n <- dataframe %>% count(Drug, Gene_Protein_Change, Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug, Gene_Protein_Change, Drug_Gene_Protein_Change) %>% filter(n == 2)
    keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
  }
  if("Drug_Gene" %in% grouping) {
    # Filter out DGs with too few samples in at least one mutation status category
    # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
    count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
    dataframe <- filter(dataframe, Drug_Gene %in% dgl_keep)
    dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
  }
  signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
  saveRDS(signif, outfile)
  return(signif)
}

@@

## Protein changes

```{r protein_change_data}
ccle_prot <- filter(prot, Database == "CCLE")
ccle_prot <- unfactorize(ccle_prot)

ctrp_prot <- filter(prot, Database == "CTRP")
ctrp_prot <- unfactorize(ctrp_prot)

gdsc_prot <- filter(prot, Drug %in% g2p_drugs & Database == "GDSC")
gdsc_prot <- unfactorize(gdsc_prot)
```

```{r prot_wilcoxon_tests, eval=FALSE}
ccle_prot <- unfactorize(ccle_prot)
ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")

ctrp_prot <- unfactorize(ctrp_prot)
ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")

gdsc_prot <- unfactorize(gdsc_prot)
gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
```

```{r load_prot_wilcoxon_rds}
ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds")
```

@@

    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) {
    signif_grid <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid < -log10(0.05)] <- NA

    signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid < -log10(0.05)] <- NA

@@

```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.03)
png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
# png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
# draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
# dev.off()
```
